### 2017-07-07 introduction.tex
working intro

While science has long been collaborative and data driven, today, more than ever before, researchers are dependent on the ability to safely store, effectively manage, and quickly analyze vast amounts of
data. Moreover, individual data-sets that are of interest to science and scholarship vary widely in size, often take on heterogeneous structures, and varying levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
data use agreements that can vary from user to user and institution to institution.

In a typical research setting, collaborators from multiple institutions often share data and techniques
for analyzing the data. Given the sensitivity of data, the security of the data is a primary concern.

>>>>

While science has long been collaborative and data driven, today, more than ever before, researchers are dependent on the ability to safely store, effectively manage, and quickly analyze vast amounts of
data. Moreover, individual data-sets that are of interest to science and scholarship vary widely in size, often take on heterogeneous structures, and command varying levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
data use agreements that can be so granular as to vary from user to user and institution to institution. At the very same time, a typical research setting involves collaborators from multiple institutions that often share data, analysis techniques, and results. Yet, when data use agreements limit access and activities and these limits are imposed at the level of individual users, research collaboration can either lead to breaches of agreement or can grind to a halt under administrative burden when data is particularly sensitive.
